MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
summary of points code updated

```
### Home Advantage analysis
```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])

>>>>

#SUMMARY OF POINTS
```{r}
ptssum<- cast(df, GAME_ID1+ player_id + player_name ~ PTS); head(ptssum)
#creating "total points per player, per game" column
ptssum$totalpts<- ptssum[,"2"]*2 + ptssum[,"3"]*3

pttsum2<-ptssum[order(ptssum$totalpts,decreasing=TRUE),]
head(pttsum2,10)

### Home Advantage analysis
```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])
